Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA

### 2022-09-01 src/tex/ms.tex
Revert to 5ee28f6
text edits

% Abstract with filler text
\begin{abstract}
Short-period double white dwarf (DWD) binaries will be the most prolific source of gravitational waves (GWs) for the Laser Interferometer Space Antenna (LISA). DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by overlapping GW signals, limiting the detectability of individual sources of all kinds. Population modeling of Galactic DWDs typically assumes a binary fraction of $50\%$ \textbf{and a log-uniform Zero Age Main Sequence (ZAMS) orbital period distribution}. However, recent observations have shown that the binary fraction of close, solar-type stars exhibits a strong anti-correlation with metallicity \textbf{which modulates the ZAMS orbital period distribution below $10^4$ days}. In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction. We simulate DWDs using the binary population synthesis suite \cosmic\ and incorporate a metallicity-dependent star formation history to create a Galactic population of short-period DWDs. We compare two models: one which assumes a metallicity-dependent binary fraction \textbf{and ZAMS orbital period distribution}, and one with a binary fraction of 50\% \textbf{and log-uniform ZAMS orbital period distribution}. \textbf{We repeat our analysis for three different assumptions for Roche-lobe overflow interactions.} We find that while metallicity impacts the evolution and intrinsic properties of our simulated DWD progenitor binaries, the LISA-resolvable populations of the two models remain roughly indistinguishable. However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction \textbf{for two of our four variations.} This effect lowers the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources. \textbf{The LISA population remains unchanged in number for two variations, highlighting the sensitivity of the population to binary evolution prescriptions.}
\end{abstract}

>>>>

% Abstract with filler text
\begin{abstract}
Short-period double white dwarf (DWD) binaries will be the most prolific source of gravitational waves (GWs) for the Laser Interferometer Space Antenna (LISA). DWDs with GW frequencies below $\sim1\,\rm{mHz}$ will be the dominant contributor to a stochastic foreground caused by overlapping GW signals.%, limiting the detectability of individual sources of all kinds. 
Population modeling of Galactic DWDs typically assumes a binary fraction of $50\%$ \textbf{and a log-uniform Zero Age Main Sequence (ZAMS) orbital period distribution}. However, recent observations have shown that the binary fraction of close, solar-type stars exhibits a strong anti-correlation with metallicity \textbf{which modulates the ZAMS orbital period distribution below $10^4$ days}. In this study we perform the first simulation of the Galactic DWD population observable by LISA which incorporates an empirically-derived metallicity-dependent binary fraction \textbf{using the binary population synthesis suite \cosmic\ and a metallicity-dependent star formation history}. 
%We simulate DWDs using the binary population synthesis suite \cosmic\ and incorporate a metallicity-dependent star formation history to create a Galactic population of short-period DWDs. 
We compare two models: one which assumes a metallicity-dependent binary fraction, %\textbf{and ZAMS orbital period distribution}, 
and one with a binary fraction of 50\%
%\textbf{and log-uniform ZAMS orbital period distribution}. 
\textbf{We repeat our analysis for three different assumptions for Roche-lobe overflow interactions.} We find that while metallicity impacts the evolution and intrinsic properties of our simulated DWD progenitor binaries, the LISA-resolvable populations of the two models remain roughly indistinguishable. However, the size of the total Galactic DWD population orbiting in the LISA frequency band is reduced by more than half when accounting for a metallicity-dependent binary fraction \textbf{for two of our four variations.} 
%This effect lowers the confusion foreground, effectively increasing the sensitivity for detecting all types of low-frequency LISA sources. 
\textbf{The LISA population remains unchanged in number for two variations, highlighting the sensitivity of the population to binary evolution prescriptions.}
\end{abstract}
